---
title: "Course 6: Capston Project Report README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Capstone Project: Final Task

The final task of this capstone project is to create a presentation based on the
outcomes of all tasks in previous modules and labs.
Your presentation will develop into a story of all your machine learning journey in this project, and it should be compelling and easy to understand.

In the next exercise, you can find a provided PowerPoint template to help you get started to
create a report in slides format. There are placeholders in the template for each of the required elements of the project,
and that instructions are provided on each slide. You need to delete and replace the placeholders with the actual content.
However, you are encouraged to add additional elements such as slides, charts, and tables.

There are a total of 70 points possible points for the final assessment,
and you will be graded by your peers, who are also completing this assignment.

The main grading criteria will be:

Uploaded your completed presentation in PDF format (2 pts)
Completed the required Introduction slide (4 pt)
Completed the required Exploratory Data Analysis slides (8 pts)
Completed the required content-based recommender system using user profile and course genres slides (6 pts)
Completed the required content-based recommender system using course similarity slides (6 pts)
Completed the required content-based recommender system using user profile clustering slides (6 pts)
Completed the required KNN-based collaborative filtering slide (6 pts)
Completed the required NMF-based collaborative filtering slide (6 pts)
Completed the required neural network embedding based collaborative filtering slide (6 pts)
Completed the required collaborative filtering algorithms evaluation slides (6 pts)
Completed the required Conclusion slide (6 pts)
Applied your creativity to improve the presentation beyond the template (4 pts)
Displayed any innovative insights (4 pts)
You may find more instructions in the PPT template. Also, you will
not be judged on your English language, including spelling, or grammatical mistakes.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
